---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

R code for Diffusion Tube Data Evaluation.

__DTEval__ is a package of R code used for the pro-processing, analysis and 
evaluation of diffusion tube (DT) data typically collected in air quality 
assessment exercises. 

## Project Webpages

__DTEval__ Projects pages: [to be build once package is PUBLIC]

## Installation

Get developer's version of __DTEval__ from [GitHub](https://github.com)  ([archive](https://github.com/karlropkins/AQEval)) [currently PRIVATE]:

```{r, eval=FALSE}
# (if you do not have remotes package, install it from CRAN) 
# install.packages("remotes")
remotes::install_github("karlropkins/DTEval") 
```

If you have the __DTEval__ .tar.gz file:

```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_local(file.choose()) # and select
```

## Background
This package contains code developed as part 
of an on-going project.

## Contributing
Contributions are very welcome.  

## License
GPL-3 

## Example

```{r}
require(DTEval)
```

### Get local reference data for York: 

```{r, warning=FALSE, message=FALSE}
#AURN sites: YK10-11
#AQE sites: YK7-9, YK13, YK15-16
#(using openair and dplyr) 

ref.york <- dplyr::bind_rows(
  openair::importAURN(c("YK10", "YK11"), year=2005:2023, meta=TRUE),
  openair::importAQE(c("YK7", "YK8", "YK9", "YK13", "YK15", "YK16"), 
                     year=2005:2023, meta=TRUE)
)
```

### Compare DT and reference data

```{r}
#DT data packaged as dt.york 
#source City of York Council / York Open Data
#https://data.yorkopendata.org/dataset/diffusion-tubes-data 
#(downloaded 2024-12-02)

testTubeAccuracy(dt.york, ref.york, 
                 tube="measurement", ref="no2", 
                 facet="site.ref", 
                 group="CalendarYear==2017")
```


(not keeping this example BUT maybe wrong units in 2017?)
