---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

R code for Diffusion Tube Data Evaluation.

__DTEval__ is a package of R code used for the pro-processing, analysis and 
evaluation of diffusion tube (DT) data typically collected in air quality 
assessment exercises.  

## Project Webpages

__DTEval__ Projects pages: [to be build]

## Installation

Get developer's version of __DTEval__ from [GitHub](https://github.com)  ([archive](https://github.com/karlropkins/DTEval)):

```{r, eval=FALSE}
# (if you do not have remotes package, install it from CRAN) 
# install.packages("remotes")
remotes::install_github("karlropkins/DTEval") 
```

If you have the __DTEval__ .tar.gz file:

```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_local(file.choose()) # and select
```

## Background
This package contains code developed as part of an on-going project, 
and is currently open for beta-testing. 


## Contributing
Contributions are very welcome.  

## License
GPL-3 

## Introduction Slides 

[currently here](https://github.com/karlropkins/DTEval/blob/main/docs/slides/DTEval-Introduction.pdf)

